Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-21 draft.tex

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
 $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

@@

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace. 
\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

>>>>

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.

\brian{let's start with a strict representative $B$. 
So we have an actual locally constant factorization algebra.}

\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
 \brian{How about $\ul{B}$ instead?}

\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

@@

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace.

\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}
